peter_models

### 2024-12-07 peter_models.qmd
updating OLR and MLR model

ord_mod_interactions <- polr(Q29 ~ Q271_reordered + race_recoded + age_recoded +
            rural + # Rural or Urban/Suburban
            sex_orientation + # Sexual Orientation
            educ + # Educational Attainment
            S3B + # Gender
            S7 + # Nativity
            Q21, # Party affiliation
          data = dataset_clean, Hess=TRUE)

@@

# ensure outcome variable is a factor but not ordered
dataset_clean$Q29_unordered <- factor(dataset_clean$Q29, ordered = FALSE)

# Fit multinomial model
m_mult <- multinom(Q29_unordered ~ Q271 + race_recoded + age_recoded +
            rural + # Rural or Urban/Suburban
            sex_orientation + # Sexual Orientation
            educ + # Educational Attainment
            S3B + # Gender
            S7 + # Nativity
            Q21, # Party affiliation
          data = dataset_clean)

@@

# Calculate predicted probabilities
pred_data <- expand.grid(
    Q271_simple = seq(1, 5, by = 0.1),
    race_recoded = unique(dataset_clean$race_recoded)
)

@@

# Plot for each outcome level
p2 <- ggplot(pred_long, 
             aes(x = Q271_simple, y = probability, color = race_recoded)) +
    geom_line() +
    facet_wrap(~interest_level) +
    theme_minimal() +
    labs(title = "Predicted Probabilities by Outcome Level",
         x = "Importance of Racial Identity",
         y = "Probability",
         color = "Race/Ethnicity") +
    theme(legend.position = "bottom")
print(p2)

>>>>

ord_mod_interactions <- polr(Q29 ~ Q271_reordered + race_recoded +
                  age_recoded +
            educ +  # Educational Attainment
            S3B + # Gender
            Q21, # Party affiliation
          data = dataset_clean, Hess=TRUE)

@@

# ensure outcome variable is a factor but not ordered
dataset_clean$Q29_unordered <- factor(dataset_clean$Q29, ordered = FALSE)
dataset_clean$Q271_simple <- as.numeric(dataset_clean$Q271)

# Fit multinomial model
m_mult <- multinom(Q29_unordered ~ Q271 + race_recoded + age_recoded +
            # rural + # Rural or Urban/Suburban
            # sex_orientation + # Sexual Orientation
            educ + # Educational Attainment
            S3B + # Gender
            # S7 + # Nativity
            Q21, # Party affiliation
          data = dataset_clean)

@@

# Calculate predicted probabilities
pred_data <- expand.grid(
    Q271 = unique(dataset_clean$Q271),
    age_recoded = unique(dataset_clean$age_recoded),
    race_recoded = unique(dataset_clean$race_recoded),
    educ = unique(dataset_clean$educ),
    S3B = unique(dataset_clean$S3B),
    Q21 = unique(dataset_clean$Q21)
)

@@

# Plot for each outcome level
p2 <- ggplot(pred_long, 
             aes(x = Q271, y = probability, color = race_recoded)) +
    geom_line() +
    facet_wrap(~interest_level) +
    theme_minimal() +
    labs(title = "Predicted Probabilities by Outcome Level",
         x = "Importance of Racial Identity",
         y = "Probability",
         color = "Race/Ethnicity") +
    theme(legend.position = "bottom")
print(p2)
